%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}


% job listing environments
\newenvironment{jobshort}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    }
    {
    }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[3.75pt]
    \end{tabularx}
    \begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt,label=--]
    }
    {
    \end{itemize}
    \end{minipage}    
    }



%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Lin Chen} \\[7.5pt]
\href{https://npu-chenlin.github.io/}{\raisebox{-0.05\height}\faGlobe\ npu-chenlin.github.io} \ $|$ \ 
\href{https://scholar.google.com/citations?user=SNbO7HUAAAAJ}{\raisebox{-0.05\height}\faGraduationCap\ Google Scholar} \ $|$ \ 
\href{https://orcid.org/0000-0001-8330-9369}{\raisebox{-0.05\height}\faIdCard\ ORCID} \ $|$ \ 
\href{mailto:npuchenlin@mail.nwpu.edu.cn}{\raisebox{-0.05\height}\faEnvelope \ npuchenlin@mail.nwpu.edu.cn} \ $|$ \ 
\raisebox{-0.05\height}\faMapMarker \ Shaanxi, China \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Research Summary
\section{Research Summary}
Fourth-year Ph.D. candidate specializing in computer vision and robotics with expertise in 3D reconstruction, SLAM, and differentiable rendering. Research interests include open-vocabulary environment representation and Vision-Language-Action (VLA) models. Technical Lead at multiple startups developing commercial SLAM and 3D reconstruction solutions for UAV clusters, bridging theoretical research with practical industry applications.


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2022 - 2026 & Ph.D. in Aeronautical and Astronautical Science and Technology at \textbf{Northwestern Polytechnical University} \hfill \normalsize (Expected 2026) \\
& School of Aeronautics, Advisor: Prof. Shuhui Bu \\

2019 - 2022 & M.S. in Vehicle Operation Engineering at \textbf{Northwestern Polytechnical University} \hfill \normalsize (Postgraduate Recommendation) \\
& School of Aeronautics \\

2015 - 2019 & B.E. in Aircraft Design and Engineering at \textbf{Northwestern Polytechnical University} \\
& School of Aeronautics \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Selected Publications}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{CoMA-SLAM: Collaborative Multi-Agent Gaussian SLAM} & \hfill AAAI 2025 (Under Review) \\
\multicolumn{2}{@{}X@{}}{\textbf{Lin Chen}, Yongxin Su, et al. First distributed multi-agent Gaussian SLAM framework with 99.8\% bandwidth reduction.} \\
\end{tabularx}

\vspace{0.5em}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{GauS-SLAM: Dense RGB-D SLAM with Gaussian Surfels} & \hfill arXiv 2025 \\
\multicolumn{2}{@{}X@{}}{Yongxin Su, \textbf{Lin Chen}, et al. Dense RGB-D SLAM system using 2D Gaussian surfels with superior tracking precision.} \\
\end{tabularx}

\vspace{0.5em}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{G²-Mapping: General Gaussian Mapping for Multiple Systems} & \hfill IEEE TASE 2025 \\
\multicolumn{2}{@{}X@{}}{\textbf{Lin Chen}, Boni Hu, et al. General method supporting monocular, RGB-D, and LiDAR-Inertial-Visual systems.} \\
\end{tabularx}

\vspace{0.5em}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{CODE: COllaborative Visual-UWB SLAM} & \hfill IEEE IROS 2025 \\
\multicolumn{2}{@{}X@{}}{\textbf{Lin Chen}, Xuan Jia, et al. Collaborative online dense mapping system for multiple UAVs with UWB measurements.} \\
\end{tabularx}

\vspace{0.5em}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{RTSfM: Real-Time Structure From Motion for Sequential Aerial Images} & \hfill IEEE TGRS 2021 \\
\multicolumn{2}{@{}X@{}}{Yong Zhao, \textbf{Lin Chen}, et al. Online sequential SfM solution for high-frequency aerial images with novel precision.} \\
\end{tabularx}

\vspace{0.5em}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{CurriculumLoc: Cross-Domain Geolocalization} & \hfill IEEE TGRS 2024 \\
\multicolumn{2}{@{}X@{}}{Boni Hu, \textbf{Lin Chen}, et al. Multistage refinement framework for cross-domain geolocalization.} \\
\end{tabularx}

\vspace{0.5em}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{DenseFusion: Large-Scale Online Dense Mapping} & \hfill IEEE IROS 2020 \\
\multicolumn{2}{@{}X@{}}{\textbf{Lin Chen}, Yong Zhao, et al. Large-scale online dense point cloud and DSM mapping method for UAVs.} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{joblong}{Technical Lead, Shanghai CVLife Technology}{Aug 2024 - Present}
\item Collaborated with Computer Vision Life platform on 3DGS and LIVO integration
\item Led development of SLAMiBot laser-vision product with LiDAR+Camera+RTK fusion
\item Implemented hardware-synchronized triggering and multi-sensor data acquisition
\item Developed mobile applications, scanning gimbals, and LIVO-3DGS post-processing software
\end{joblong}

\begin{joblong}{Technical Lead, Xi'an SIBITU Intelligent Technology}{Mar 2022 - Present}
\item Leading development of real-time mapping solutions based on SLAM and SfM technologies
\item Generated orthoimages, elevation maps, and 3D point clouds in real-time for UAV systems
\item Developed multi-UAV collaborative reconstruction systems for large-scale mapping
\item Deployed solutions across Linux and Windows platforms with x64/aarch64 architectures
\end{joblong}

\begin{jobshort}{Independent Quantitative Trading}{Feb 2023 - Present}
Developed fully automated quantitative trading system including data acquisition, strategy development, backtesting, and live trading execution with comprehensive performance analysis.
\end{jobshort}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Computer Vision &  \normalsize{3D Gaussian Splatting, SLAM, Structure from Motion, Dense Reconstruction, Differentiable Rendering}\\
Robotics  &  \normalsize{LiDAR-Visual-Inertial Odometry, Multi-UAV Systems, Real-time Mapping, Sensor Fusion}\\  
Programming &  \normalsize{C++, Python, CUDA, ROS, OpenCV, PyTorch, Real-time Systems}\\
Hardware &  \normalsize{UAV Systems, LiDAR+Camera+RTK Integration, Multi-sensor Synchronization}\\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}